Playing with functions on iGen study claims/values:

Source "data": http://genhq.wpengine.com/wp-content/uploads/2016/01/iGen-Gen-Z-Tech-Disruption-Research-White-Paper-c-2016-Center-for-Generational-Kinetics.pdf

So here, what I tried to do was set up what the population values might look like from this genHQ paper regarding GenZ. Study methodology stated that survery was administered to two populations: mainsample and oversample. In the mainsample, 1000 respondents were of age 14-69, while in oversample, 250 were of age 14-17, for a totalsample of 1250.

```{r}
library(ggplot2)
set.seed(1)
mainsample <- as.vector(sample(x = 14:69, 1000, replace = TRUE))
oversample <- as.vector(sample(x = 14:17, 250, replace = TRUE))
totalsample <- c(mainsample, oversample)

labels <- cut(totalsample, breaks = c(-Inf, 20, 34, 52, Inf), labels = c("GenZ","Millenials","GenX", "Boomers"))
age_df <- data.frame(labels, sample_ages)

qplot(totalsample, fill = labels)

```

```{r}
qplot(labels, fill = labels, xlab ="")
```

To find out the exact size of populations, using table function:

```{r}
table(age_df$labels)
```

Using plyr's count function:

##Setting this to a value for future use
```{r}
library(plyr)
gen_counts <- count(age_df, "labels")
gen_counts
```

